Democratizing MPC

### 2017-10-11 OaklandSubmission/intro.tex
1.1

In this work, we develop and implement our framework \tool where the programmer writes a high level C-like program (instead of a circuit) to describe the function to be computed. Our compiler automatically converts this program to a suitable SMC protocol that uses both arithmetic and boolean secure computation components as well as the correct conversion protocols whenever required. Our compiler is general and can work with any secure implementation of a mix of arithmetic and boolean computations. In our work, we focus on semi-honest secure two-party computation and  ABY \cite{aby} provides the suitable cryptographic back-end. \divya{We provide a formal type system.... } We evaluate our system on various benchmarks such as logistic regression and convolutional neural network (CNN) for MNIST data \cite{minionn}, naive bayes, decision trees from \cite{shafindss}. Evaluations show that protocols generated by our compiler match the performance of hand-crafted protocols in most cases (see \ref{sec:eval}). \divya{Below, we will  give an overview of \tool and describe our contributions.}

@@

\subsection{\tool: Overview and Contributions} Write high level overview of programming language and tool..

\divya{ideally have small paragraphs about key features}
1. ease to programming.. refer to section with example in our language; contrast to verilog paper; programmer is completely oblivious of security; looks like a normal/vanilla/ regular C program;
Moreover, the developer does not write keywords such as secret and public; 
\input{fig-ex-aby}
\input{fig-ex-sml}

>>>>

In this work, we develop and implement our framework \tool for secure computation that achieves generality, performance and programmer productivity. The programmer writes a high level C-like program (instead of a circuit) to describe the function to be computed. Our compiler automatically generates an SMC protocol using a mix of Arithmetic and Boolean compute. Our compiler is general and can work with any secure implementation of a mix of arithmetic and boolean computations. In our work, we focus on semi-honest secure two-party computation. We build on ABY \cite{aby} that provides the suitable cryptographic back-end in this setting. We provide a formal type system and prove correctness and security of our compiler. We evaluate our system on various benchmarks such as logistic regression and convolutional neural network (CNN) for MNIST data \cite{minionn}, naive bayes, decision trees from \cite{shafindss}. Evaluations show that protocols generated by our compiler match the performance of hand-crafted protocols in most cases (see \sectionref{sec:eval}). \divya{Below, we will  give an overview of \tool and describe our contributions in more detail.}

@@

\subsection{\tool: Overview and Contributions} 
\label{sec:contrib}
Write high level overview of programming language and tool.. \divya{have some preamble}

\tool is a programmer-friendly framework to express the function to be computed and uses a mix of arithmetic and boolean SMC back-ends. We illustrate the above toy example of $w^Tx >0$ in our language in \figureref{ex-sml}. As is clear from the code, the programmer is not required to write keywords such as {\em secret} or {\em public} and can remain completely oblivious of the cryptographic back-end. In contrast, \figureref{ex-aby} illustrates the same example using the framework in ABY \cite{aby}. Here, as already mentioned, the programmer needs to write the low level gates like $\mathrm{MULT, ADD, CONS, GT}$, etc. The programmer is also required to use the appropriate share conversion gates such as A2Y that converts Arithmetic shares to Yao shares.

Our compiler is aware of cryptographic costs of different representations and inter-conversions.  Based on these costs, our compiler, given a program in \tool, automatically picks Arithmetic and Boolean representations for different sub-parts of the program and inserts the required inter-conversions as well. 
Our experiments show that automatically generated protocols using \tool match the performance of tailor-made protocols in \cite{minionn,shafindss} (see \sectionref{eval}). This shows that  \tool achieves generality, performance and programmer productivity. These features allow us to evaluate our system on a variety of benchmarks, especially, state-of-the-art ML prediction algorithms with \emph{real} data and models.

We give a formal {\em type system} for our language and prove useful properties. We prove that if a program type checks in our language then it would run correctly, e.g., there would not be any array index out of bounds error. The programmer writes a single code describing the inputs from each party and the function to be computed. Our compiler automatically generates separate executables for the server and the client that can be executed in the distributed setting. We prove the {\em correctness} for this compilation, i.e., the outputs obtained in the distributed execution are identical to the stand-alone execution by a trusted third party. We formally reduce the {\em security} of our system to the security of the cryptographic back-end. For details on correctness and security theorems see \sectionref{ld-proofs}.

Another issue in adoption of SMC is difficulty in scaling to large programs. 
%In general, SMC implementations struggle in scaling to large programssize of memory on a system limits the largest compute inside the SMC and hence,. 
The reason being all SMC implementations use a circuit-like representation as an intermediate representation. Hence, the largest compute that can be done securely is upper-bounded by the amount of memory on a machine.

\input{fig-ex-aby}
\input{fig-ex-sml}

\newpage
\divya{ideally have small paragraphs about key features}
1. ease to programming.. refer to section with example in our language; contrast to verilog paper; programmer is completely oblivious of security; looks like a normal/vanilla/ regular C program;
Moreover, the developer does not write keywords such as secret and public;
